---
title: "Prof. Olga's Class - September 8, 2025"
output: pdf_document
date: "2025-09-05"
---

Dear prof. Olga. How are you? I hope i did a good job in this task. It was challenging, because I've missed the R workshop, but I'll try my best.

1 - How many Korean Dramas are included in this list? Write an R code to respond to this question.
```{r}
db_kdrama <- read.csv("kdrama.csv") #Open K-Drama database
sum(!is.na(db_kdrama$Name)) #Count the arrows in the "Name" colum
#I also used !is.na ro eliminate NA values
```
2 - Use an R code to return a list of variables that are included in this dataset.
```{r}
names(db_kdrama) #Return the name of the variables in the database
```
3 - Use an R code to identify what the mean value of total number of episodes for all the kdramas in the dataset is.
```{r}
mean(db_kdrama$Number.of.Episodes)
```
4 - Plot a histogram of the shows rating.
```{r}
hist(db_kdrama$Rating, xlim = c(8.3, 9.3), ylim = c(0, 120),
       xlab = 'Rating', ylab = 'Frequency',
       main = 'Frequency of K-Drama grading',
       col = 'red', border = "black")
# I used hist to produce the histogram, xlim and ylim to define de limit values of the axis
# xlab and ylab to change labels, main to change the name of the histogram
# col and border to change colors
```
We can personalize the histogram in interesting ways, such as:
```{r}
#First, install the jpeg package
install.packages("jpeg")
#Run the package
library(jpeg)
#Criate the object for an image (I made it for the K-drama "Crash Landing on You" or 
#"Sarangui Bulsichak")
pousandonoamor <- readJPEG("chuudoloona.jpg")
#Then, create an empty plot
plot(1, type = "n", xlim = c(0, 1), ylim = c(0, 1), axes = FALSE, xlab = "", ylab = "")
#Add the image to the plot
rasterImage(pousandonoamor, xleft = 0, ybottom = 0, xright = 1, ytop = 1)
#Allow plot over image
par(new = TRUE)
#Plot the original histogram
hist(db_kdrama$Rating, xlim = c(8.3, 9.3), ylim = c(0, 120), 
     xlab = 'Rating', ylab = 'Frequency', main = 'Frequency of K-Drama grading', 
     col = 'red', border = "black") # Plot your histogram
```

5 - How many shows have a rating higher than 9 points? Show how you calculated that in R.
There are different ways to calculate that in R.
```{r}
#we can use the following code to return how many show have more than 9
sum(db_kdrama$Rating > 9) #excludes shows with exactly 9 rating
sum(db_kdrama$Rating >= 9) #counts shows with 9 and more than 9

# you can also use dplyr to create a database only with the shows rated greater than R
install.packages("dplyr") #install and load dplyr package
library(dplyr)

#we can use filter to create de database with shows rated 9 or greater
kdrama_g9 <- filter(db_kdrama, Rating >= 9)
dplyr::glimpse(kdrama_g9) #used to see the new database 
# I don't know why View function is not working, so let's use this code

#Using the new database, we can discover the grade of "Crash Landing on You"
crash_row <- kdrama_g9 %>% filter(Name == "Crash Landing on You")
  crash_rating <- crash_row$Rating
  print(crash_rating)
```
It's rated 9, I almost guessed it right!

6 - Rename variable Year.of.release to simply Year without creating a new variable
```{r}
newdb_kdrama <- db_kdrama %>% 
  rename(Year = Year.of.release)
names(newdb_kdrama)
```
7 - How many shows in this dataset were released in 2020-2022? Demonstrate with an R code.
```{r}
kdrama_2022 <- db_kdrama %>%
  filter(Year.of.release >= 2020 & Year.of.release <= 2022)
  dim(kdrama_2022)
```
106 shows were released in the 2020-2022 period!

8 - What type does the variable Duration have? Show with an R code.
```{r}
class(db_kdrama$Duration)
```

9 - Recode variable Duration so that it would be a numerical variable measuring duration in minutes. Plot the histogram of the recoded variable (though one).
```{r}
# We will need to install and load "stringr" package
install.packages("stringr")
library(stringr)
# I'll use the function str_extract to remove the "hr." and "min." from observations
# I'll use is.na to check whether hours or minutes are absent, and change it for zero
# Extract hours, returns NA if not found
hours <- as.numeric(str_extract(db_kdrama$Duration, "\\d+(?= hr\\.)"))
# Turns NAs into 0
hours[is.na(hours)] <- 0
# Extract minutes, returns NA if not found
minutes <- as.numeric(str_extract(db_kdrama$Duration, "\\d+(?= min\\.)"))
# Turns NAs into 0
minutes[is.na(minutes)] <- 0
# Turns everything into minutes
total_min <- hours * 60 + minutes

#Plot the data into a histogram
hist(total_min, xlim = c(7, 101), ylim = c(0, 120), 
     xlab = 'Duration in minutes', ylab = 'Frequency', 
     main = 'Distribution of K-Drama episodes duration', 
     col = 'red', border = "black")
```

10 - Create a new dataset that will include shows with Original.Network being Netflix.
```{r}
# I use str_detect to find Netflix in observations that include other networks
netflix_shows <- db_kdrama %>%
    filter(str_detect(Original.Network, "Netflix"))
```
11 - What is the average rating score for the shows that have Netflix as an Original Network.
```{r}
mean(netflix_shows$Rating)
```

